TBA

### 2020-08-25 manuscript.tex
Updates from Overleaf

Over the last couple decades, DNA has proved to be much more than a vessel for genetic information. From sensing, to computing, to directed self-assembly, the programmable and predictable nature of DNA has unlocked numerous unforeseen applications \citep{Seeman2017DNANanotechnology, Adleman1994MolecularProblems.pdf, Rothemund2006FoldingPatterns, Gu2010ALine}. Recently, structural DNA nanotechnology has enabled self-assembly on micro to milli scales, and dynamic DNA nanotechnology has been used to perform basic calculation and to probe single molecules via temporal DNA signatures\citep{MhatreV.HoJi-AnnLee2012NIHAccess, Bui2018, Shah2019}. \noter{Please correct reference ``MhatreV.HoJi-AnnLee2012NIHAccess''} Both technologies rely on the hybridization reaction between complementary DNA strands and leverage the flexibility of shorter DNA oligomers to participate in these reactions. Although many experimental and computational studies have rigorously explored DNA dynamical phenomena such as hybridization, hairpin formation, and single base pair flipping, the sequence-dependent mechanisms of hybridization and dissociation dynamics are not fully understood \citep{Yin2011KineticsHybridization, Xiao2019, Hinckley2014Coarse-grainedEffects, Sanstead2016, Porschke1971CooperativeTransition, Porschke1973ThermodynamicsPairs, Chen2007InfluenceHybridization, Craig1971ElaxationOligon}. Moreover, it is unclear the extent to which these processes evolve in an "all-or-nothing" fashion or if an ensemble meta-stable states facilitates the transition. Recent breakthrough studies have coupled experimental techniques with machine learning and MD simulations to investigate and predict sequence-dependent kinetics \citep{Schickinger2018TetheredHelices, Zhang2018PredictingSequence}. Where these studies focus on association and dissociation kinetics alone, we broaden our analysis into higher order dynamical processes and meta-stable intermediates. The stability of certain intermediates states, such as out-of-register or  base pairing in repetitive sequences, has been well documented in previous computational studies \citep{Phys2014, Xiao2019}). Furthermore, frayed structures and dynamics have been investigated in numerous computational and experimental studies \citep{Zgarbova2014BaseRNA, Nonin1995TerminalFraying, Nikolova2012ProbingSimulations, Andreatta2006UltrafastHelix}. Sandstead et al. highlighted the role of these dynamics during duplex dissociation, where the stability of frayed states was dictated by G:C bond placement in the 10-mer oligonucleotide sequence \citep{Sanstead2016}. In this work, we study the same four sequences explored by Sandstead et al in an effort to uncover the sequence-dependent dynamics and their relation to  metastable structures mentioned above.

@@

\section{\label{sec:Results}Results}
- lead with same kind of diagram for each sequence, add additional figures when necessary for a given sequence

>>>>

Over the last couple decades, DNA has proved to be much more than a vessel for genetic information. From sensing, to computing, to directed self-assembly, the programmable and predictable nature of DNA has unlocked numerous unforeseen applications \citep{Seeman2017DNANanotechnology, Adleman1994MolecularProblems.pdf, Rothemund2006FoldingPatterns, Gu2010ALine}. Recently, structural DNA nanotechnology has enabled self-assembly on micro to milli scales, and dynamic DNA nanotechnology has been used to perform basic calculation and to probe single molecules via temporal DNA signatures\citep{MhatreV.HoJi-AnnLee2012NIHAccess, Bui2018, Shah2019}. \noter{Please correct reference ``MhatreV.HoJi-AnnLee2012NIHAccess''} Both technologies rely on the hybridization reaction between complementary DNA strands and leverage the flexibility of shorter DNA oligomers to participate in these reactions. Although many experimental and computational studies have rigorously explored DNA dynamical phenomena such as hybridization, hairpin formation, and single base pair flipping, the sequence-dependent mechanisms of hybridization and dissociation dynamics are not fully understood \citep{Yin2011KineticsHybridization, Xiao2019, Hinckley2014Coarse-grainedEffects, Sanstead2016, Porschke1971CooperativeTransition, Porschke1973ThermodynamicsPairs, Chen2007InfluenceHybridization, Craig1971ElaxationOligon}. Moreover, it is unclear the extent to which these processes evolve in an "all-or-nothing" fashion or if an ensemble meta-stable states facilitates the transition. Recent breakthrough studies have coupled experimental techniques with machine learning and MD simulations to investigate and predict sequence-dependent kinetics \citep{Schickinger2018TetheredHelices, Zhang2018PredictingSequence}. Where these studies focus on association and dissociation kinetics alone, we broaden our analysis into higher order dynamical processes and meta-stable intermediates. The stability of certain intermediates states, such as out-of-register or  base pairing in repetitive sequences, has been well documented in previous computational studies \citep{Phys2014, Xiao2019, Maciejczyk2014DNAModel}) \textcolor{purple}{No experimental has been done to hint at these dynamics (difficult to differentiate from fraying), but they've been discuss in many computational works and seem likely to occur}. Furthermore, frayed structures and dynamics have been investigated in numerous computational and experimental studies \citep{Zgarbova2014BaseRNA, Nonin1995TerminalFraying, Nikolova2012ProbingSimulations, Andreatta2006UltrafastHelix}. Sandstead et al. highlighted the role of these dynamics during duplex dissociation, where the stability of frayed states was dictated by G:C bond placement in the 10-mer oligonucleotide sequence \citep{Sanstead2016}. In this work, we study the same four sequences explored by Sandstead et al in an effort to uncover the sequence-dependent dynamics and their relation to  metastable structures mentioned above.

@@

\section{\label{sec:Results}Results}
